Full text search hack with Shiny/R

### 2015-12-26 article.rmd
Starting to add more intelligence when downloading files. Needs fix.

As we can observ on the previous examples, the query extension algorithm has some noisy produced by the double query
generated in order to join  the results.

>>>>

As we can observ on the previous examples, the query extension algorithm has some noisy produced by the double query
generated in order to join  the results. Also, it won't matter if you have the exact match twice, as the algorithm does not
focus on the exact matches, instead it will relate the occurrences on the first search (where the match happens) and the
sencond (where the algorithm searches for the words that appear in the same phrase than the exact match). That means 
that it is possible to have a high rank without have any matching occurrence.

This kind of searches is useful if you want to find entries with words that appear frequently within your search.
